Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-05-18 review/response-letter.tex

{\color{blue}

{\hspace*{-4.5em}{[R1:4]}\vspace*{-1.9em}}

Thank you for the concern regarding the readability of the figure. We have split the figure to address the concern into two Figures, 6 and 7. Subfigures that are related are then on a separate row, each for one case. I,II in Figure 6 are related to CPP at boundary values of path parameters and varying atmospheric conditions, and i,ii Figure 7 are related to planning-scheduling of I,II with varying battery conditions. We have rewritten the captions, adding additional commentary to ease the understanding.

\begin{formal}
  \footnotesize
  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations. In {\color{red}a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}. In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions. In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}

@@

{\hspace*{-4.5em}{[R1:12]}\vspace*{-1.9em}}

Thank you for noticing that a citation and clarification are missing regarding the energy models. The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}3}) and Equation ({\color{red}4}) are equal under some conditions (the value of the initial guess is described by Equation ({\color{red}9}) and the model is not perturbed by the control).

We have elaborated further in Section III-A to reflect the observation and added a reference to the corresponding author's previous work.

\begin{formal}
  {\color{black}
  [...] {\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
  models in Eqs.~({\color{red}3}--{\color{red}4}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
  and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$}}
    {\color{blue}\begin{equation}\tag{9}
    {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
    \end{equation}}
    %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
  %\end{lem}
  %\begin{proof}
  %The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
  %\end{proof}
  %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies. {\color{blue}Further details are proposed in the first author's Ph.D. thesis~[{\color{green}31}]}.
  }
  \vspace*{1ex}
\end{formal}
}

@@

9. By Definition III.2, $g(\cdot)$ has two variables, but equation (12) only has one variable. I assume a time variable is missing

{\color{blue}

{\hspace*{-4.5em}{[R1:14]}\vspace*{-1.9em}}

Thank you for noticing the issue. We use the predictive layer function $g(\cdot)$ to return the energy of any possible configuration of computation parameters, independently of the time, given a measuring device (i.e., the computing hardware can measure the energy of different components such as overall, CPU, GPU, memory, etc.).

To construct the predictive layer, we utilize a discrete set of measuring layers $\mathbf{g}(\cdot)$, each containing the time in the form of an interval that specifies for how long a given configuration on a measuring device has to be profiled.

The two variables of $g$ are then the configuration and the specific measuring device, indicated by a positive integer value.
We have not realized there might arise confusion between $\mathbf{g}$ and $g$ and thus decided to use $\gamma$ for the measuring layer instead of $\mathbf{g}$ and add further commentary after the equation.

\begin{formal}
  \color{black}
  [...] notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. {\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~({\color{red}13})}.
  \vspace*{1ex}
\end{formal}

@@

11. The way that the authors define $\tau_{i,j}$ and $\nu_{i,j}$ in (10a) and (10b) implies path parameter $c_{i,j}$, $j\in\{1,2,\dots,\rho\}$ contributes equally to $t_s$ (defined in line 24 in Algorithm 2). It is difficult to determine if this assumption is reasonable, since $\rho=1$ in the numerical simulations.

{\color{blue}

{\hspace*{-4.5em}{[R1:16]}\vspace*{-1.9em}}

Thank you once again for underlying this point. The assumption was not clearly stated in the manusctipt, and we have thus added additional commentary before the equations.

\begin{formal}\color{black}
  {\color{blue}W}e assume that the coverage time evolves linearly{ \color{blue}and that the }path parameters{ \color{blue}contribute to it equally.} $c_i^\rho$ can be {\color{blue}then} transformed into a time measure with scaling factors 
  [...]
  \vspace*{1ex}
\end{formal}
}

@@

  In addition, what is the performance metric we want to observe improving using the algorithm 2 in the numerical experiments (comparing i, ii to I, II baselines)?

  {\color{blue}

  {\hspace*{-4.5em}{[R2:4]}\vspace*{-1.9em}}

  Thank you for noticing the comparison was missing in the manuscript. We utilize as a performance metric the weighted average configuration of parameters against the battery state of charge at the end of the flight. We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.

  \begin{formal}
    {\color{blue}
Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, {\color{red}I} would not be able to complete the flight, and {\color{red}II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of {\color{red}i} and {\color{red}ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}  
    \vspace*{1ex}
  \end{formal}
  }

@@

  Average results from more numeric experiments (e.g., average flights competed on baseline vs. with new algorithm) would also really benefit the paper. Paper would also be greatly strengthened by actual physical experiments on UAV.

  {\color{blue}

  {\hspace*{-4.5em}{[R2:6]}\vspace*{-1.9em}}

  Thank you for this point; we have reduced the number of experimental results due to space constraints. Nonetheless, we agree that additional results would further justify the need for planning-scheduling in the aerial robotics domain. To this end, we have added the average result for eight flights derived utilizing the flight simulation capabilities of the open-source Paparazzi flight controller. These results are derived in two equally sized sets, each similar to flights i and ii in the manuscript. The results are described thoroughly in the corresponding author's Ph.D. thesis (reference [{\color{green}31}], Section 6.3.2.

  We have altered the numerical simulation section accordingly.

  \begin{formal}
    {\color{blue}
    Additional results are reported~[{\color{green}31}] utilizing simulation capabilities of the Paparazzi flight controller. Data are split into two sets of four flights each, one similar to {\color{red}i} and the other to {\color{red}ii}, i.e., initial parameters are at boundary configurations.
    These results have an average performance metric of 1.81 and 1.24 for flights similar to {\color{red}i} and {\color{red}ii} respectively.}

    \vspace*{1ex}
  \end{formal}
  }

@@

- ``the Zamboni motion [40], but additionally allows variable CPP at the very core of this work.'' -- need to clarify more why Algorithm 1/Zamboni-like motion is different from Zamboni motion. What is the   insight that allows the Zamboni motion to be recalculated/replanned at each stage that isn't possible with regular Zamboni motion in reference [40]?

{\color{blue}

{\hspace*{-4.5em}{[R2:7]}\vspace*{-1.9em}}

Thank you for underlying this point. We have not realized that it was not clear in the original manuscript. We use the concept of path parameters as inputs to the path functions that compose the coverage path to ultimately alter the coverage quality dynamically, throughout the flight.

We have added explanatory text to Section IV-A to make this point clear.

\begin{formal}
  \color{black}
  [...] It is similar to another motion in the literature, the \emph{Zamboni motion}~[{\color{green}41}], but additionally allows variable CPP %at the very core of this work
  {\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
  {\color{blue} Although cover variability is already considered in the literature~[{\color{green}41}], it is limited to boustrophedon motion for rotary wings.}
  The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~{\color{red}II.5}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$. [...]% (see Fig.~\ref{fig:zambo}).
  \vspace*{1ex}
\end{formal}
}

@@

- Figure 1 not clear; are we supposed to be able to differentiate between i, ii, and iii paths? Not able to differentiate currently, so unable to understand key takeaway of figure. What is the meaning of the colors (green for i, red for ii/iii)?

{\color{blue}

{\hspace*{-4.5em}{[R2:9]}\vspace*{-1.9em}}

Thank you for noticing the issue regarding poor clarity. We have altered the figure and added a legend to clarify the meaning of i, ii, and iii as different stages in planning-scheduling.

\begin{formal}
\color{black}
  {\color{blue}\scriptsize \input{../figures/il_abs_new_review.tikz}}
  {\color{black}\footnotesize%Illustrative example of planning-scheduling. 
  Fig.~1:~The figure shows an initial plan~(in~{\color{red}i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~{\color{red}ii}) and changing the number of fly-bys or other motion aspects~(in~{\color{red}sth:iii}). 
  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
  the spectrum analysis of the energy data, revealing the periodicity %of the data 
  exploited in the %overall 
  energy model.
  %Follow the collected energy data of a physical aerial robot flying the static coverage.
  }
  \vspace*{1ex}
\end{formal}

@@

{\color{blue}

{\hspace*{-4.5em}{[R2:11]}\vspace*{-1.9em}}

Thank you for underlying the issue. We have attempted to optimize the space but overloaded the figure and significantly reduced its readability. We have reordered Figure 6 to address the issue. We have first split the figure into two Figures, 6 and 7. In both, we utilize one row per case. Figure 6 contains cases I and II related to static coverage at the two boundary configurations under varying wind speeds and directions.

\begin{formal}
  \footnotesize
  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations. In {\color{red}a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}. In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions. In {\color{red}c} are the states that compose the energy model for {\color{red}I}.}
\end{formal}

@@

Overall, the paper addresses a very interesting topic and brings together many different techniques to solve a challenging problem. It could be strengthened with more attention to clarity to convey the technical insights and more experiments showing an improvement in a performance metric of interest.

{\color{blue}

{\hspace*{-4.5em}{[R2:12]}\vspace*{-1.9em}}

Thank you once again for the commentary as well as for bringing up a lot of important points. We are indeed excited about the potential of planning-scheduling for the aerial robotics domain to address autonomy and other criticalities arising in a number of use cases. We would like to propose a revised version of the manuscript for your kind consideration, where we incorporate the points and additional experimental results.}

### 2022-05-18 energy-planning.tex
implemented ALL the reviewers comments

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{1}}$, and Ulrik Pagh Schultz$^{\text{1}}$
  %\thanks{This work is supported and partly funded by the European Union's Horizon2020 research and innovation program under grant agreement No. 779882 (TeamPlay).}
  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S., H. S. M.,  and U. P. S. are with the Unmanned Aerial Systems Center, M{\ae}rsk Mc-Kinney M{\o}ller Institute, University of Southern Denmark, Odense. Email: {\tt\footnotesize ads@mmmi.sdu.dk};} 
  \thanks{$^{\text{2}}$H. G. is with the Faculty of Physics, Department of Computer Architecture and Automatic Control, Universidad Complutense de Madrid, Spain.}
  \thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). 
  Bottom-left shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here. Bottom-right shows a spectrum analysis of the energy data, revealing the periodicity of the data exploited in the overall energy model.
  %Follow the collected energy data of a physical aerial robot flying the static coverage.
  }
  \label{fig:il-abs}
  \vspace*{-4ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

@@

{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
%\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
  {\color{blue}\begin{equation}
  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
  \end{equation}}
  %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
%\end{lem}
%\begin{proof}
%The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
%\end{proof}
%Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
i.e., $h,y$ are both harmonic signals with the same frequencies{\color{blue}~\cite{seewaldphdthesis}}.

@@

For ease of notation, we assume that the coverage time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$).

@@

\begin{defn}[Measurement layer]\label{def:meas}
  Given a measuring device, computation parameters, and initial and final time instants, the \emph{measurement layer} is the function $\mathbf{g}:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
\end{defn}

@@

The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules. Additionally, the \powprof{} tool supports the battery SoC detailed in Section~\ref{sec:mod-bat}. The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. The measuring device in both $\mathbf{g}$ and $g$ is implicit.

@@

To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius. It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP at the very core of this work. 
{\color{blue} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}
The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).

>>>>

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
  \thanks{The work was partly funded by E.U. grant No. 779882 (TeamPlay); H. G. work is supported by Ramon y Cajal grant No. RYC2020-030090-I.}
  %\thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  %\thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S. is with the Dept. of Mech. Eng. and Mater. Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS. Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
  \thanks{$^{\text{2}}$H. G. is with the Dept. of Comput. Archit. and Technol., University of Granada, Spain;} 
  \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
  University of Southern Denmark.}
  %\thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

\begin{figure}[t]
  \centering
  \vspace*{-9.8ex}
 %\begin{tikzpicture}
 %  \node[inner sep=0pt] () at (0,0)
        {\color{blue}\scriptsize \input{\figpath/il_abs_new.tikz}}
 %  \node[inner sep=0pt] () at (-2,-5.67)
 %      {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
 %  \node[inner sep=0pt] () at (2.1,-5.67)
 %      {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
 %\end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-bys or other motion aspects~(in~\ref{sth:iii}). 
  {\color{blue}Top-right} shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here{\color{blue}; below is }%. Bottom-right shows 
  the spectrum analysis of the energy data, revealing the periodicity %of the data 
  exploited in the %overall 
  energy model.
  %Follow the collected energy data of a physical aerial robot flying the static coverage.
  }
  \label{fig:il-abs}
  \vspace*{-4ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, whereas the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
%\begin{ctb}
%  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
%\end{ctb}

@@

{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
%\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
  {\color{blue}\begin{equation}
  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
  \end{equation}}
  %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
%\end{lem}
%\begin{proof}
%The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
%\end{proof}
%Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
i.e., $h,y$ are %both 
harmonic signals with the same frequencies{\color{blue}. Further details are proposed in the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.

@@

%For ease of notation, 
{\color{blue}W}e assume that the coverage time evolves linearly{ \color{blue}and that the }path parameters{ \color{blue}contribute to it equally.} $c_i^\rho$ can be {\color{blue}then} transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$).

@@

\begin{defn}[Measurement layer]\label{def:meas}
  Given a measuring device, computation parameters, and initial and final time instants, the \emph{measurement layer} is the function $\gamma:\mathbb{Z}_{>0}\times\mathbb{Z}^\sigma\times\mathcal{T}\rightarrow\mathbb{R}$ that returns an energy measure.
\end{defn}

@@

The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules. Additionally, the \powprof{} tool supports the battery SoC detailed in Section~\ref{sec:mod-bat}. The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\gamma(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\gamma(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. {\color{blue}M}easuring device in $\gamma$ and $g$ is {\color{blue}not explicitly stated in Eq.~(\ref{eq:piece-wise-reg})}.

@@

To address fixed wings and aerial robots generally, this section details a different motion with a wide turning radius. It is similar to another motion in the literature, the \emph{Zamboni motion}~\cite{araujo2013multiple}, but additionally allows variable CPP %at the very core of this work
{\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
{\color{blue} Although cover variability is already considered in the literature~\cite{difranco2015energy}, it is limited to boustrophedon motion for rotary wings.}
The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~\ref{def:primitive}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$.% (see Fig.~\ref{fig:zambo}).
